Joshua 2.0: A Toolkit for Parsing-Based Machine Translation \\with Syntax, Semirings, Discriminative Training and Other Goodies

### 2010-04-23 papers/wmt10/joshua-progress.tex
Added Juri's section
git-svn-id: https://joshua.svn.sourceforge.net/svnroot/joshua/branches/publications@1638 0ae5e6b2-d358-4f09-a895-f82f13dd62a4

\section{Support for Syntax Augmented MT}
\todo{juri or ccb}

>>>>

\section{Support for Syntax-Augmented MT}
The syntax-augmented approach to hierachical phrase-based machine
translation introduced by \newcite{samt2006} aims at improving
translation quality by introducing syntactic information into the
decoding process. To this end, one side of the bitext is parsed and a
syntax-augmented grammar containing additional nonterminal symbols is
extracted. These new symbols are obtained by annotating the
nonterminals in Hiero-style rules
\begin{center}
\begin{tabular}{c}
  {\small \tt [X]} $\Rightarrow$ {\small \tt [X,1]} sans {\small \tt [X,2]} 
  $\vert$ {\tt \small [X,1]} without {\small \tt [X,2]} \\
\end{tabular}
\end{center}
extracted from the bitext, the nonterminals are labeled according
to what constituents cover the nonterminal span on the parsed side of
the bitext. 
\begin{center}
\begin{tabular}{c}
  {\small \tt [NP] $\Rightarrow$  ne [V,1] pas | did not [V,1] } \\
  {\small \tt [VP] $\Rightarrow$  a b [V,1] | c d [X,1] } 
\end{tabular}
\end{center}
To ensure good coverage, SAMT concatenates syntactic constituents or
uses CCG-style labels when there is no single constituent covering a
span. The resulting grammar allows for derivations that take into
account the syntactic
